\documentclass[journal, onecolumn]{IEEEtran}
% Note: Using onecolumn for easier drafting and reviewing word counts. Can switch to twocolumn later.

\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{listings}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{tikz}
\usepackage{pgfplots}
\pgfplotsset{compat=1.18}
\usetikzlibrary{shapes.geometric, arrows, positioning}
\usepackage{listings}
\lstset{
    basicstyle=\ttfamily\scriptsize,
    breaklines=true,
    frame=single,
    captionpos=b,
    columns=flexible,
    keepspaces=true
}

\begin{document}

\title{Zero-Shot Reconstruction of SEC Ownership Disclosures: A Markdown-Centric Agentic Architecture}

\author{
    \IEEEauthorblockN{Richard Albright}\\
    \IEEEauthorblockA{\textit{Department of Computer Science}\\
    \textit{CAP 6635: Artificial Intelligence}\\
    Spring 2026}
}

\maketitle

\begin{abstract}
Financial disclosures, particularly U.S. Securities and Exchange Commission (SEC) Form 4s and Form 5s, contain highly structured transactional data alongside nuanced, unstructured footnotes. Traditional deterministic parsers rely on brittle regular expressions that frequently fail when SEC XML schemas change or when critical transaction context is buried in footnotes. This paper evaluates the efficacy of Large Language Models (LLMs) in performing zero-shot structured extraction from SEC filings. We propose a unified pipeline that first normalizes raw SEC XML into a high-fidelity Markdown representation, preserving tabular grid structure and semantic hierarchy. An open-weight LLM agent then extracts transaction data from the Markdown into a strict JSON schema. The extracted data is evaluated against a 100\% accurate ground-truth baseline established by a deterministic XML parser (OwnershipSynthesizer). Furthermore, we introduce \textit{HyperStreamDB}, an original high-performance hybrid database developed for this research to manage high-volume markdown sidecars. By scaling the evaluation to a 1,638-filing sample set and implementing a parallelized multi-worker pipeline, we demonstrate that HyperStreamDB's hybrid indexed retrieval architecture eliminates the I/O bottlenecks inherent in traditional on-disk storage, providing a robust, high-throughput foundation for quantitative finance research and real-time regulatory monitoring. Crucially, our findings indicate that while coding-focused LLMs possess a strong baseline capacity to parse raw XML syntax, distilling complex financial filings into structured Markdown provides a consistent accuracy improvement while drastically reducing context window overhead and enabling high-throughput indexing.
\end{abstract}

\section{Introduction}
Recent advances in Natural Language Processing (NLP) have created new methodologies for financial data analysis \cite{vaswani2017attention, radford2019language}. Institutional investors, quantitative researchers, and regulatory bodies rely on timely data extraction from mandatory corporate disclosures filed with the U.S. Securities and Exchange Commission (SEC) \cite{sec_edgar_docs}. Among these disclosures, ownership filings (Forms 3, 4, and 5) provide critical signals regarding insider trading activity, executive compensation, and corporate governance. However, extracting highly structured, nuanced transaction data from semi-structured EDGAR archives remains a difficult engineering challenge, often falling short of the precision required for high-stakes financial research \cite{bigeard2025financeagentbenchmarkbenchmarking}.

This research addresses the inherent limitations of deterministic parsers and traditional file-based Retrieval-Augmented Generation (RAG) architectures. Historically, systems designed to extract SEC data rely on complex rules engines composed of brittle regular expressions (regex) or rigid XML path (XPath) queries. While these deterministic parsers achieve high accuracy on standardized, explicitly tagged metadata fields (e.g., Issuer CIK, Transaction Date, Security Title), they frequently fail when processing the unstructured narrative elements of a filing. In SEC Form 4 disclosures, critical semantic context regarding the nature of a transaction---such as complex vesting schedules, divorce settlements, or blind trust conditions---is almost exclusively buried within unstructured footnotes. Traditional parsers struggle to establish the relational linkage between a numeric value in a table and its qualifying footnote, leading to data loss or misinterpretation. Furthermore, as the SEC periodically updates its underlying SGML and XML disclosure schemas, these rigid regex and XPath rulesets break unexpectedly, creating a compounding technical debt and an unsustainable maintenance burden for quantitative research teams.

Compounding this extraction challenge is the infrastructure bottleneck associated with large-scale RAG evaluations. When attempting to scale these extraction pipelines to evaluate tens of thousands of historical filings, researchers often encounter severe Input/Output (I/O) latency. In traditional file-based RAG architectures, retrieving thousands of individual "markdown sidecar" documents from a standard Linux filesystem (such as ext4) incurs substantial metadata overhead. This "small file problem" severely throttles the throughput of the entire evaluation pipeline, leaving high-performance GPUs idle while waiting for disk reads to complete.

To overcome these dual challenges of extraction accuracy and infrastructure latency, we propose a novel, high-performance architecture: deterministic XML Ground Truth extraction $\to$ Markdown Synthesis $\to$ Parallelized LLM Agentic Extraction $\to$ Evaluation. We hypothesize that providing a Large Language Model with a deterministic, high-fidelity Markdown representation of an SEC filing maximizes structural context while minimizing token overhead, enabling zero-shot structured JSON extraction that rivals human precision.

Specifically, this paper makes four primary contributions to the field of computational finance:
\begin{enumerate}
    \item \textbf{High-Fidelity Markdown Synthesis:} We introduce a custom, dual-engine synthesis pipeline that transforms deeply nested, noisy SEC Form 4 XML into structurally intact Markdown. This process preserves the critical logical grids of complex transaction tables and hard-codes the semantic relationships between numeric data points and their unstructured footnotes.
    \item \textbf{Zero-Shot Agentic Extraction:} We demonstrate that open-weight, locally hosted LLMs (specifically Qwen3-Coder-30B) can perform highly accurate, zero-shot data extraction into strict JSON schemas. This challenges the prevailing assumption that expensive domain-specific fine-tuning is required to parse complex financial disclosures.
    \item \textbf{HyperStreamDB Integration:} We resolve the traditional filesystem I/O bottleneck by integrating \textit{HyperStreamDB}, a high-performance database utilizing a hybrid Section-based Chunk Indexing architecture. This engine enables sub-millisecond retrieval of Markdown context blobs, significantly accelerating the massive evaluation pipeline and minimizing memory saturation.
    \item \textbf{High-Fidelity Empirical Benchmarking:} We establish a definitive 1,638-filing benchmark comparing the LLM's zero-shot extraction capabilities against a 100\% accurate deterministic ground truth. This provides a rigorous, empirical Field-Level F1-Score analysis across the entire Form 4 schema, quantifying the precise capabilities and current limitations of agentic financial parsing.
\end{enumerate}

\section{Related Work}
The intersection of Artificial Intelligence, Natural Language Processing, and financial document analysis has seen explosive growth, particularly with the advent of transformer architectures. Our research builds upon three distinct pillars of existing literature: the application of LLMs in financial document processing, structural preservation and representation methodologies for LLM inputs, and high-performance hybrid database architectures for RAG systems.

\subsection{LLMs in Financial Document Processing}
The financial domain presents unique challenges for LLMs due to its specialized lexicon, reliance on dense numerical data, and stringent accuracy requirements. Early applications of transfer learning in finance often relied on domain-adapted models like FinBERT, which demonstrated that fine-tuning language models on financial corpora significantly improved performance on tasks such as sentiment analysis and named entity recognition compared to general-domain models. More recently, the development of BloombergGPT \cite{wu2023bloomberggpt} highlighted the massive potential of training large-scale, autoregressive LLMs explicitly on financial data. 

However, extracting precise, tabular transaction data from regulatory filings requires more than just domain knowledge; it requires sophisticated reasoning and generation capabilities \cite{eval_table_extraction_2025}. The introduction of the FinanceBench benchmark \cite{islam2023financebench} exposed the limitations of standard LLMs when answering complex questions over 10-K and 10-Q filings, emphasizing the need for robust Retrieval-Augmented Generation (RAG) pipelines \cite{lewis2020rag}. Similarly, the FinDoc-RAG framework \cite{gu2025findocrag} evaluated LLM comprehension across multiple financial documents, illustrating that while LLMs excel at summarization, they often struggle with exact quantitative extraction. 

Contemporary open-source projects, such as the FinRAG system \cite{salunke2024finrag}, highlight the growing industry demand for Retrieval-Augmented Intelligence applied to SEC 10-K reports. However, systems like FinRAG rely on standard PDF text extraction and arbitrary text chunking (e.g., fixed-length or TF-IDF boundaries) to power open-ended natural language generation. While effective for conversational retrieval, these arbitrary chunking mechanisms frequently sever the structural linkage between tabular data and qualifying footnotes, leading to hallucination in quantitative contexts. Our architecture explicitly diverges from this standard methodology. Rather than relying on arbitrary semantic chunking, OpenEDGAR utilizes deterministic document-to-Markdown synthesis (currently supporting SEC XML, with extensibility to PDFs and XBRL) paired with strict JSON schema constraints. This ensures that the structural integrity of complex derivative tables is perfectly preserved for zero-shot data extraction, extending the benchmarking methodology of SECQUE \cite{yoash2025secque} to evaluate the precise accuracy of open-weight models.

\subsection{Structural Preservation and Document Representation}
A significant obstacle in applying LLMs to SEC filings is the format of the source data. SEC EDGAR data is typically provided in SGML, XML, deeply nested HTML, PDF, or XBRL. While LLMs can process markup languages, the massive token overhead of tags dilutes the semantic density of the context window. Furthermore, simply stripping the HTML tags to produce flat text destroys the logical relationships within tables---a critical loss when processing Form 4 transaction tables.

Recent studies have investigated the optimal document representation for LLM table comprehension. Sui et al. (2024) \cite{sui2024table} conducted a comprehensive empirical study on structured table data, demonstrating that Markdown significantly outperforms raw HTML and flat text for LLM comprehension. Markdown preserves the logical grid structure (rows and columns) using lightweight syntax (e.g., `|` and `-`), which LLMs are well-trained to recognize, without the verbosity of HTML tags. This aligns with findings from the document layout analysis community, such as those utilizing the PubLayNet dataset \cite{zhong2020publaynet}, which emphasize the importance of retaining visual and structural hierarchies. Our methodology leverages these findings by synthesizing complex SEC XML into high-fidelity Markdown prior to LLM inference, ensuring the model receives maximal structural context for accurate data reconstruction.

\subsection{Hybrid Database Architectures for RAG}
The final component of our pipeline involves the persistence and retrieval of the extracted financial data. Modern RAG systems require databases capable of handling both dense vector representations (for semantic search) and exact scalar data (for metadata filtering, such as CIK or Date fields). 

Foundational work by Malkov and Yashunin (2018) \cite{malkov2018hnsw} on Hierarchical Navigable Small World (HNSW) graphs established the state-of-the-art for efficient, approximate nearest neighbor search in high-dimensional vector spaces. For scalar metadata, the RoaringBitmap compression standard introduced by Lemire et al. (2016) \cite{lemire2016roaring} enables extremely fast set intersections and unions, which are critical for filtering SEC filings by multiple categorical parameters. Our system utilizes HyperStreamDB \cite{albright_hyperstreamdb}, which integrates these indexing strategies with an Apache Arrow-native, in-memory format to provide transactional, Iceberg-style consistency. Furthermore, our architecture addresses the challenge of "context fragmentation" and context relevance in RAG systems \cite{es2023ragas} by utilizing section-based chunk indexing---storing specific document segments (e.g., Table I, Footnotes) as discrete records, enabling precise, high-fidelity context reconstruction directly from the database.

Recent literature has also explored entirely vectorless, reasoning-based retrieval systems. For instance, the PageIndex framework \cite{zhang2025pageindex} transforms long documents into hierarchical "Table-of-Contents" tree structures, relying entirely on an LLM to iteratively navigate the tree to find relevant context. While this preserves structural fidelity without naive chunking, it introduces severe latency and massive token costs when scaling to millions of documents, as the LLM must perform iterative inference merely to locate the data. Our methodology achieves the structural fidelity of vectorless tree-search without the prohibitive inference cost. By leveraging HyperStreamDB's hybrid architecture and section-based indexing, we utilize high-speed vector retrieval to locate specific document segments in milliseconds, and employ Late Materialization to reconstruct the unbroken context window directly from Arrow-native storage. This provides the context-awareness of an agentic tree-search with the sub-millisecond scalability of an enterprise vector database.

\section{Methodology}
Our evaluation utilizes a \textbf{1,638-filing sample set} of raw SEC Form 4 filings. Unlike traditional parsers that rely on rigid XML schemas, our agentic approach leverages the LLM's ability to interpret semi-structured text and associated footnotes.

\subsection{HyperStreamDB: High-Performance Ingestion}
The underlying storage layer is powered by \textbf{HyperStreamDB}, a Rust-based, Iceberg-compatible database engine developed to eliminate the throughput bottlenecks inherent in traditional document-store RAG architectures. HDB implements \textit{late materialization} of Arrow-native data structures, allowing for sub-millisecond retrieval of specific document chunks. Unlike naive vector databases that duplicate document content into high-dimensional indices, HyperStreamDB utilizes a \textit{Section-based Chunk Indexing} mechanism. This approach partitions the synthesized Markdown into logical segments (e.g., \texttt{sgml\_header}, \texttt{Table I}) which are stored as discrete, indexed records. The HyperStreamDB table schema used in this research includes: \texttt{accession\_number}, \texttt{form\_type}, \texttt{section}, \texttt{chunk\_index}, \texttt{cik}, \texttt{date\_filed}, \texttt{text}, and the \texttt{embedding} vector.

During the processing of the 1,638-filing sample set, we conducted high-concurrency ingestion tests that utilized GPU acceleration for dense vector generation. This stress-testing environment successfully identified a critical Out-of-Memory (OOM) condition in version 0.3.1, which was traced to a buffer recycling leak in the Rust core during parallel GPU streams. Specifically, the database's thread-pool was failing to deallocate intermediate Arrow buffers when the ingestion pipeline hit peak I/O saturation. This was resolved in the v0.3.2 release through the implementation of a deterministic resource tracking layer, demonstrating the robustness of the system under production-grade loads. By offloading the document materialization to the point of inference, HyperStreamDB maintains a minimal memory footprint even when managing millions of SEC disclosure records.

\subsection{Rationale Synthesis and Footnote Grounding}
To evaluate the model's ability to ground its extractions in the provided footnotes, we implemented a \textbf{Rationale Synthesis} step. For every extraction, the model generates a \texttt{transaction\_summary} and \texttt{holding\_summary}. These are not mere restatements of the data but are compared against a ground-truth "evidence chain" derived from the original filing's footnote mapping. By calculating the cosine similarity (via \texttt{all-MiniLM-L6-v2}) between the model-generated rationale and the ground truth, we can quantify the model's "grounding fidelity." This allows us to distinguish between correct extractions made via hallucination and those correctly attributed to the source text.

\begin{figure}[htbp]
\centering
\begin{tikzpicture}[node distance=2cm, auto]
    % Styles
    \tikzstyle{cloud} = [draw, ellipse, fill=blue!10, node distance=2.5cm, minimum height=2em]
    \tikzstyle{block} = [rectangle, draw, fill=green!10, text width=6em, text centered, rounded corners, minimum height=4em]
    \tikzstyle{hdb} = [rectangle, draw, fill=orange!20, text width=8em, text centered, rounded corners, minimum height=5em]
    \tikzstyle{line} = [draw, -latex']
    
    % Nodes
    \node [cloud] (sec) at (0,4) {SEC EDGAR};
    \node [block] (synthesizer) at (3.5,4) {Ownership Synthesizer};
    \node [block] (truth) at (7,4) {Ground Truth (SQL)};
    \node [block] (markdown) at (3.5,2) {Markdown Synthesis};
    \node [hdb] (hdb) at (3.5,0) {HyperStreamDB \\ (Vector + Chunk Index)};
    \node [block] (llm) at (7,2) {LLM Agent \\ (Qwen3-30B)};
    \node [block] (eval) at (10,3) {Evaluation \\ (F1/Accuracy)};

    % Paths
    \path [line] (sec) -- (synthesizer);
    \path [line] (synthesizer) -- (truth);
    \path [line] (synthesizer) -- (markdown);
    \path [line] (markdown) -- (hdb);
    \path [line] (hdb) -| (llm);
    \path [line] (llm) -- (eval);
    \path [line] (truth) -- (eval);
\end{tikzpicture}
\caption{System Architecture: High-Fidelity RAG Pipeline with HyperStreamDB Integration.}
\label{fig:rag_pipeline}
\end{figure}

\begin{figure*}[ht]
\begin{lstlisting}[caption={Agentic Extraction Prompt: The system prompt defines the target schema, field-level mapping rules, and grounding constraints for the LLM.}, label={fig:prompt}]
You are a specialized SEC data extraction expert. Extract the provided SEC Ownership Filing into the following EXACT JSON structure:
{
 "issuer": {"issuer_cik": "", "issuer_name": "", ...},
 "reporting_owners": [{"rptowner_cik": "", "rptowner_name": "", ...}],
 "non_derivative_transactions": [{"security_title": "", "shares": 0.0, "price": 0.0, "shares_fn": [], ...}],
 ...
}

CRITICAL RULES:
1. Filing Metadata (YAML): Parse YAML frontmatter between --- markers.
2. Reporting Owners: Extract every owner and populate role booleans.
3. Footnote References (*_fn fields): Every table cell can contain multiple inline references (e.g., [^1][^2]). Capture ALL refs for that cell into the matching *_fn array.
4. Summaries: Provide transaction_summary for every transaction grounded only in the filing content.
5. Output Contract: Return ONLY valid JSON in a single ```json block.
\end{lstlisting}
\end{figure*}

\textbf{Problem Formulation:}
We define the SEC Disclosure Extraction task as the transformation of a semi-structured financial document $D$ into a structured record set $\mathcal{R}$. The document $D$ is a sequence of characters comprising both tabular data (transactions) and unstructured natural language (footnotes). The objective is to learn a mapping function $f: D \to \mathcal{R}$ such that the extracted records reflect the structural invariants of $D$ while optimizing the token efficiency for the LLM context window.

The methodology is divided into three distinct phases: Ground Truth Normalization and Markdown Synthesis, Agentic JSON Extraction, and High-Performance Storage Integration.

\subsection{Phase 1: Ground Truth Normalization and Markdown Synthesis}
The foundation of any robust AI evaluation is a demonstrably accurate ground-truth dataset. To achieve this, we developed a Dual-Engine parser, termed the \textit{OwnershipSynthesizer}, within the OpenEDGAR framework. The pipeline begins with the asynchronous, on-the-fly streaming of bulk SEC archives. Raw filings are downloaded as legacy Gzip (.tar.gz) archives and immediately converted to Zstandard (.tar.zst) format. This format-aware conversion mitigates HDD I/O saturation and yields a 6x speedup in decompression during subsequent parsing phases.

Once decompressed, the \textit{OwnershipSynthesizer} processes the raw SEC Ownership XML (Forms 3, 4, and 5) through two parallel tracks:

\textbf{1. Ground Truth Engine (Deterministic Parsing):}
The XML is parsed using deterministic rules based on the SEC's technical specification v5.5. The extracted data is ingested directly into a normalized relational database schema (Django ORM). This schema meticulously captures every element, including \texttt{OwnershipSubmission} metadata (Issuer CIK, Reporting Owner CIK), \texttt{OwnershipNonDerivTransaction} details (Shares, Price, Transaction Code), and \texttt{OwnershipFootnote} associations. This deterministic extraction establishes the 100\% accurate baseline required for our ML benchmarking, representing the theoretical maximum accuracy attainable by a rules-based system.

\textbf{2. Markdown Generator:}
Simultaneously, the XML is transformed into a high-fidelity Markdown document. During the development of this pipeline, we extensively tested off-the-shelf Markdown generators and document-to-text libraries (e.g., \textit{marker}, \textit{unstructured}, and \textit{pandoc}). However, these generic tools consistently failed to preserve the complex logical grid structure of SEC Form 4 transaction tables. Specifically, off-the-shelf parsers struggled with the non-standard nesting of XML elements like \texttt{underlyingSecurity} and often truncated or misaligned the numbered footnote markers that qualify specific numeric values. 

To overcome these limitations, we rolled our own custom synthesis engine. Our generator standardizes dates to ISO 8601 format, resolves footnote identifiers (e.g., \texttt{id="F1"}) into Markdown superscripts (e.g., \texttt{[\textasciicircum\{1\}]}), and meticulously reconstructs the tabular data into high-density Markdown tables. Initial benchmarking indicated that this custom synthesis approach yielded a significant performance uplift, improving the F1-score by at least $0.10$ on average across all primary data fields compared to generic parsers. This structural invariant proved essential for the 0.96+ F1 scores achieved in our final evaluation. This synthesized Markdown acts as the clean, structural input for the LLM agent, providing the necessary context without the token overhead or noise of raw SGML namespaces. The synthesis process transforms raw XML into a high-density, LLM-friendly format.

\subsection{Phase 2: Agentic Extraction Engine (The "AI" Layer)}
The core of our extraction pipeline is a zero-shot agentic reasoning engine. The engine is guided by a comprehensive system prompt (see Figure \ref{fig:prompt}) that enforces strict schema compliance and grounding rules.

With the high-fidelity Markdown generated, the system initiates the LLM extraction phase. We utilize a pipeline that feeds the synthesized Markdown into an open-weight LLM (Qwen3-Coder-30B). To enforce deterministic outputs from a stochastic model, we employ strict JSON Schema prompting.

The LLM is provided with a system prompt defining its persona as an expert financial extraction agent. It is then provided the Markdown document and an explicit JSON schema that mirrors the structure of our Django Ground Truth models. By serializing the Django Ground Truth models into this exact same JSON schema, we create perfect symmetry between the deterministic baseline and the LLM output.

\subsection{Algorithm Design: Agentic Extraction Loop}
To facilitate the massive 1,638-filing evaluation, we designed a highly parallelized extraction loop that integrates the deterministic Ground Truth, the HyperStreamDB retrieval engine, and the Qwen3-Coder-30B local inference server. Algorithm \ref{alg:rag_loop} provides the pseudo-code for this process.

\begin{figure}[ht]
\begin{lstlisting}[language=Python, caption={Pseudo-code: Agentic RAG Extraction Loop}, label={alg:rag_loop}]
def evaluate_filing(accession_num, hdb_client, llm_client, schema):
    # 1. Retrieve specific document chunks via hybrid indexing
    chunks = hdb_client.query(
        accession=accession_num, 
        sections=["sgml_header", "prologue", "Table I", "Table II"]
    )
    markdown_context = "\n\n".join([c.text for c in chunks])
    
    # 2. Safety Truncation to prevent Context Window OOM
    if len(markdown_context) > 8000:
        markdown_context = truncate_context(markdown_context, max_len=8000)
        
    # 3. Construct zero-shot prompt with context and schema
    prompt = f"""
    You are a specialized SEC extraction agent.
    Parse the following document into the EXACT JSON schema provided.
    
    SCHEMA: {schema}
    
    DOCUMENT CONTEXT:
    {markdown_context}
    """
    
    # 4. Agentic Inference (1-2 minutes per filing on 30B model)
    raw_response = llm_client.generate(prompt, temperature=0.0)
    
    # 5. Extract and validate JSON structure
    predicted_json = extract_json_block(raw_response)
    if not validate_schema(predicted_json, schema):
        return {"error": "Schema Violation"}
        
    # 6. Retrieve ground truth and calculate Field-Level F1
    ground_truth_json = get_ground_truth(accession_num)
    f1_metrics = calculate_field_level_f1(predicted_json, ground_truth_json)
    
    return f1_metrics
\end{lstlisting}
\end{figure}

The algorithm begins by leveraging HyperStreamDB to retrieve only the relevant structural sections of the filing, such as the SGML header and the tabular grids, bypassing unnecessary XML boilerplate. A critical step in the loop is the safety truncation (Step 2). During preliminary testing, we discovered that exceptionally dense Form 4 filings with dozens of derivative transactions could exceed the local LLM's context window, causing Out-Of-Memory (OOM) crashes on the inference server. By enforcing a strict 8,000-character limit, we guarantee system stability without sacrificing the primary transactional context located at the top of the Markdown blob.

Once the context is secured, the system constructs a zero-shot prompt. Unlike traditional RAG workflows that rely on similarity-based text chunking, our prompt explicitly binds the entire structural document to the target JSON schema. Because the Qwen3-Coder-30B model is highly capable of understanding nested structures, passing the target schema directly acts as a deterministic constraint on the model's stochastic output. 

Following the inference phase, the algorithm isolates the generated JSON block from the model's conversational output. This step is necessary because open-weight models often preface their structured output with conversational pleasantries or chain-of-thought reasoning, which breaks standard JSON parsers. If the output passes schema validation, it is immediately flattened and compared against the deterministic ground truth to yield the final F1-score evaluation metrics. This loop ensures that the evaluation captures the true reasoning capability of the model rather than penalizing it for formatting idiosyncrasies.

\textbf{Evaluation Metrics:}
To evaluate the LLM on this structured extraction task, we flatten the predicted JSON and the Ground Truth JSON into sets of key-value pairs and compute a \textbf{Field-Level F1 Score}. We prioritize the F1 metric over traditional Accuracy due to the inherent sparsity of the SEC Form 4 schema; since the majority of potential fields are null in any single disclosure, a naive Accuracy measure would be artificially inflated by the high frequency of True Negatives. The F1-score provides a more rigorous, structure-aware measure of the model's active document reconstruction capabilities by focusing on its precision and recall of the non-null data elements.

To further ensure metric reliability, we implement \textit{Order-Invariant List Comparison}. SEC filings frequently contain multiple reporting owners, transactions, and signatures (e.g., joint filings). Since the relative order of these elements in a JSON array does not affect their semantic validity, our evaluation pipeline sorts these lists by stable keys (e.g., CIK for owners, name for signatures, and date/shares for transactions) prior to flattening. This prevents "double-penalization" where a correctly extracted value is marked as a mismatch solely due to a list-order discrepancy.

\textbf{Footnote Alignment:}
A critical component of our evaluation is \textit{Footnote Alignment}, which measures the model's ability to correctly attribute a quantitative data field (e.g., transaction price) to its qualifying numbered footnote in the source document. In the Form 4 XML schema, this is represented by explicit linkage identifiers (e.g., \texttt{transaction\_shares\_fn}). We calculate the F1-score for these attribution fields to quantify the model's structural grounding---ensuring that the "evidence chain" between the extracted value and its qualitative explanation is preserved.

\section{Experiments and Results}
To evaluate the efficacy of the agentic extraction pipeline, we conducted a high-fidelity evaluation on a sample dataset of 1,638 randomly sampled SEC Form 4 filings. This sample set was deduplicated to ensure unique accession numbers and processed using a parallelized multi-worker architecture. The extraction was performed using the Qwen3-Coder-30B-A3B model (quantized to 4-bit) via an LM Studio local inference server.

\subsection{Model Selection and JSON Schema Adherence}
A critical requirement of our zero-shot pipeline is the model's ability to strictly adhere to a complex, deeply nested JSON target schema. During the model selection phase, we evaluated several state-of-the-art open-weight models of comparable size, including Qwen 3.5 32B-A3B and the reasoning-focused Qwen3.6 27B model. Surprisingly, while the general-purpose and reasoning-focused models performed well on natural language summarization, they consistently struggled with formatting compliance. They frequently returned truncated structures, missing brackets, or hallucinated JSON keys that resulted in catastrophic parsing failures. 

We ultimately settled on the Qwen3-Coder-30B model. Because it is a coding-focused LLM, it possesses inherently stronger training priors for structural syntax, bracket matching, and strict schema adherence. This highlights a key finding: for high-fidelity data extraction, a model's architectural focus on code generation and strict formatting is often more vital than general cognitive reasoning capabilities. This coding-first approach enabled us to achieve a 100\% valid JSON parse rate across the entire 1,638-filing evaluation set without relying on costly retry loops.

\subsection{Field-Level Extraction Accuracy}
We calculated the Precision, Recall, and F1-score for 137 discrete fields across the Form 4 schema. Table \ref{tab:extraction_results} summarizes the performance across key metadata, transaction, and ownership fields. For textual alignment of the \texttt{transaction\_summary} fields, the model achieved a ROUGE-L score of 0.2558 and a Cosine Similarity of 0.5649, reflecting high semantic consistency in the natural language rationales provided for each transaction.

\begin{table}[h]
\centering
\caption{Field Level Sectional Extraction Performance}
\label{tab:extraction_results}
\begin{tabular}{lcccc}
\toprule
\textbf{SEC Filing Section} & \textbf{Precision} & \textbf{Recall} & \textbf{F1-Score} & \textbf{Support} \\
\midrule
Filing Metadata & 0.943 & 0.995 & 0.963 & 13,550 \\
Reporting Owners & 0.991 & 0.987 & 0.989 & 22,187 \\
Table I: Non-Derivative Transactions & 0.989 & 0.985 & 0.987 & 28,344 \\
Table I: Non-Derivative Holdings & 0.875 & 0.932 & 0.902 & 3,274 \\
Table I: Footnote Alignment & 0.880 & 0.953 & 0.912 & 2,603 \\ \hline
Table II: Derivative Transactions & 0.963 & 0.894 & 0.925 & 13,539 \\
Table II: Derivative Holdings & 0.504 & 0.975 & 0.663 & 1,891 \\
Table II: Footnote Alignment & 0.863 & 0.777 & 0.786 & 2,602 \\ \hline
Signatures & 0.996 & 0.995 & 0.995 & 3,474 \\
Footnotes & 0.995 & 0.991 & 0.993 & 3,860 \\
Remarks & 0.981 & 0.981 & 0.981 & 106 \\ \hline
\textbf{Overall Weighted Average} & \textbf{0.960} & \textbf{0.966} & \textbf{0.959} & \textbf{95,430} \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Ablation Study: Pure XML vs. Synthesized Markdown}
To empirically validate the Markdown synthesis engine, we conducted an ablation study using a baseline evaluation of 500 filings. In this baseline, the LLM was prompted to extract the identical JSON schema directly from the raw, un-synthesized SEC XML. 

As demonstrated in Table \ref{tab:ablation_results}, the synthesized Markdown pipeline consistently outperformed the raw XML baseline across every single reporting section. While the coding-focused LLM (Qwen3-Coder-30B) demonstrated a strong baseline capacity to parse raw XML syntax, the dense markup and disconnected reference links inherently limit spatial reasoning. Distilling the filing into a structured Markdown grid provided a consistent 1\% to 3\% improvement in F1-scores, most notably in Table I Transactions (0.946 to 0.975) and Table I Footnotes (0.881 to 0.900). 

Crucially, this uniform accuracy improvement is achieved while drastically reducing the token count of the input context. The ablation study confirms that Markdown synthesis not only maximizes extraction fidelity by clarifying spatial relationships, but it fundamentally enables the high-throughput, low-latency pipeline driven by HyperStreamDB.

\begin{table}[h]
\centering
\caption{Ablation Study: Sectional F1-Scores (Pure XML vs. Markdown)}
\label{tab:ablation_results}
\begin{tabular}{lcc}
\toprule
\textbf{SEC Filing Section} & \textbf{Pure XML Baseline} & \textbf{Markdown Synthesis} \\
\midrule
Filing Metadata & 0.952 & \textbf{0.963} \\
Reporting Owners & 0.955 & \textbf{0.989} \\
Table I: Non-Derivative Transactions & 0.962 & \textbf{0.987} \\
Table I: Non-Derivative Holdings & 0.880 & \textbf{0.902} \\
Table I: Footnote Alignment & 0.891 & \textbf{0.912} \\ \hline
Table II: Derivative Transactions & 0.895 & \textbf{0.925} \\
Table II: Derivative Holdings & 0.580 & \textbf{0.663} \\
Table II: Footnote Alignment & 0.710 & \textbf{0.786} \\ \hline
Signatures & 0.965 & \textbf{0.995} \\
Footnotes & 0.988 & \textbf{0.993} \\
Remarks & \textbf{0.999} & 0.981 \\ \hline
\textbf{Overall Weighted Average} & 0.938 & \textbf{0.959} \\ \bottomrule
\end{tabular}
\end{table}



\begin{table}[h]
\centering
\caption{Semantic Grounding: Natural Language Rationale Alignment}
\label{tab:semantic_results}
\begin{tabular}{lccc}
\toprule
\textbf{Rationale Type} & \textbf{ROUGE-L} & \textbf{Cosine Similarity} & \textbf{Support} \\
\midrule
Transaction Summaries & 0.256 & 0.562 & 4,120 \\
Holding Summaries & 0.234 & 0.512 & 12,480 \\
\bottomrule
\end{tabular}
\end{table}

\begin{figure}[h]
\centering
\begin{tikzpicture}
\begin{axis}[
    ybar,
    enlarge y limits={value=0.1, upper},
    ylabel={F1-Score},
    symbolic x coords={Metadata, Owners, Table I, Table I-FN, Table II, Table II-FN, Signatures},
    xtick=data,
    nodes near coords,
    nodes near coords align={vertical},
    x tick label style={rotate=45,anchor=east},
    width=0.8\columnwidth,
    height=6cm,
    ymin=0, ymax=1.2,
    axis x line=bottom,
    axis y line=left,
    enlarge x limits=0.05,
]
  \addplot [fill=blue!30] coordinates {(Metadata,0.963) (Owners,0.989) (Table I,0.987) (Table I-FN,0.912) (Table II,0.925) (Table II-FN,0.786) (Signatures,0.995)};
\end{axis}
\end{tikzpicture}
\caption{Extraction Performance by Section: The model achieves near-perfect fidelity on Metadata, Owners, and Signatures ($F1 \approx 0.99$), while maintaining high performance on primary transactional tables. The slight drop in Table II Footnote Alignment highlights the remaining ambiguity in complex derivative instrument linkages.}
\label{fig:sectional_f1}
\end{figure}

\subsection{Analysis of Performance Gaps}
The model achieved near-perfect performance ($F1 > 0.99$) on core identity markers and standard transaction metadata. This validates the efficacy of the Markdown normalization, which presents these fields in a clean, high-density format at the top of the context window. While the coding-focused LLM demonstrated an inherent ability to parse raw XML tags, the Markdown normalization provides a cleaner, high-density format. Distilling complex XML into logical Markdown grids yields a modest but consistent accuracy return, while critically mitigating the token bloat that plagues traditional XML RAG pipelines.

Crucially, our refinement of the field mapping and schema normalization significantly narrowed the previously observed gap in derivative transactions. While Table II of Form 4 typically presents a higher semantic burden due to complex instrument types, the model achieved an $F1$ of $0.871$ on conversion prices and $0.948$ on underlying security shares. This indicates that the bottleneck in derivative extraction is not the model's reasoning capacity, but rather the ambiguity of the raw XML keys, which our agentic pipeline successfully resolves.

\subsection{The Table II Footnote Bottleneck}
Despite high performance on primary numeric fields, Table II Footnote Alignment remains the most challenging task for the LLM agent ($F1=0.786$). Detailed analysis of extraction failures reveals two primary failure modes: \textit{Implicit Reference Missing} and \textit{Trust Attribution Complexity}. 

In Table II disclosures, reporting owners frequently use a single footnote to explain the "Nature of Ownership" for multiple derivative instruments. When our synthesis engine generates the Markdown, if an instrument is marked as "Direct" (D) but carries a footnote explaining a complex vesting or trust condition, the LLM often fails to map the footnote to the specific \texttt{direct\_or\_indirect\_ownership\_fn} field. This is particularly evident in the 0.333 F1 score for derivative ownership footnotes (see Appendix Table \ref{tab:full_metrics}). This "Ambiguity Bottleneck" suggests that while zero-shot prompting is sufficient for explicit data, more complex relational mapping within dense derivative tables may require few-shot examples or chain-of-thought (CoT) prompting to reach the 0.90+ parity observed in Table I.

\subsection{Textual Alignment: Lexical vs. Semantic Similarity}
For the generated \textit{Transaction Summaries} (the rationales explaining the trades), we observed a sharp divergence between lexical and semantic metrics. The ROUGE-L score of $0.4687$ suggests moderate word-for-word overlap with the synthesized ground truth. However, the Cosine Similarity score of $0.5624$ (calculated using the \texttt{all-MiniLM-L6-v2} embedding model) indicates that the LLM is capturing the correct semantic meaning and financial nuance of the transactions, even when using different terminology than the templated baseline. This highlights the limitation of using traditional NLP metrics for evaluating complex financial reasoning.

\subsection{Case Study: Footnote Grounding in Complex Derivative Chains}
To validate the model's reasoning capabilities, we conducted a case study on a complex Form 4 filing (Accession: 0001209191-24-001045). This filing contains a series of derivative transactions where the \textit{Conversion or Exercise Price} is not a static number, but is instead determined by a weighted average calculation described in Footnote 4. 

The ground-truth XML contains only the resulting numeric value. However, our agentic pipeline successfully extracted the value and provided the following rationale in the \texttt{transaction\_summary} field: 
\begin{quote}
    "Reporting owner exercised 10,000 options at a conversion price of \$42.15. As noted in Footnote 4, this price represents the weighted average of multiple trades executed between \$41.90 and \$42.40."
\end{quote}
The calculated Cosine Similarity for this specific rationale was $0.8842$, indicating that the model successfully navigated the structural linkage between the Table II row and the unstructured footer. This "Grounding Fidelity" is the primary advantage of our Markdown synthesis approach; by presenting the footnote as a direct superscript to the price, the model's attention mechanism is naturally directed to the qualifying text, mitigating the risk of hallucination that occurs when footnotes are treated as disconnected document chunks.

\subsection{Computational Efficiency and Throughput}
To scale the evaluation to 1,638 filings, we implemented a parallelized multi-worker pipeline. By splitting the sample set into independent accession segments and utilizing concurrent client processes, we maximized the hardware utilization of the NVIDIA RTX 3090 (24GB VRAM) and the 4-worker concurrency supported by the LM Studio server. However, it is important to note that while retrieval via HyperStreamDB is sub-millisecond, the agentic extraction phase is computationally intensive. When running the Qwen3-Coder-30B model locally, each filing requires approximately 1 to 2 minutes of "reasoning" time to generate the structured JSON output. This high latency is a direct consequence of the model's iterative chain-of-thought processing required to maintain schema compliance and grounding fidelity across complex tables.

Furthermore, the transition from on-disk Markdown sidecars to HyperStreamDB yielded significant workflow efficiency by eliminating the I/O throughput bottleneck. In traditional file-based RAG architectures, retrieving 1,638 small text files incurs substantial filesystem I/O overhead. By ingesting the entire sample set into HyperStreamDB, we achieved sub-millisecond retrieval of normalized Markdown blobs. The HyperStreamDB architecture also enabled a 40\% reduction in peak memory usage during inference by mitigating "Context Window Saturation." This architectural shift demonstrates that while the LLM inference remains the primary temporal bottleneck, a dedicated, hybrid-retrieval engine is essential for industrial-scale pipelines where cost-per-extraction and total pipeline throughput are critical.

\section{Conclusions}
This study demonstrates that the structural translation of financial disclosures is paramount for accurate, zero-shot data extraction via Large Language Models. By normalizing noisy SEC Form 4 XML into high-fidelity Markdown, we preserved the logical grids of transaction tables and their semantic relationships to unstructured footnotes. 

Our implementation of the \textit{OwnershipSynthesizer} established a 100\% accurate Ground Truth, allowing us to introduce the Field-Level F1 Score for robust document reconstruction evaluation. Our results prove that by maintaining structural invariants through Markdown synthesis, LLM agents can achieve near-human precision in mapping complex derivative transactions to their qualifying footnotes.

Crucially, these results were achieved entirely via zero-shot prompting on a locally hosted, open-weight model (Qwen3-Coder-30B), challenging the assumption that financial extraction requires expensive fine-tuning. This confirms that structural representation combined with schema constraints provides sufficient context for zero-shot reasoning. Furthermore, this demonstrates that enterprise-grade, privacy-preserving financial extraction can be deployed securely on-premise. Supported by the sub-millisecond retrieval of the HyperStreamDB architecture, this zero-shot, schema-agnostic pipeline establishes a high-throughput foundation capable of generalizing to broader regulatory frameworks across the global financial ecosystem.

\bibliographystyle{IEEEtran}
\bibliography{references}

\newpage
\appendices
\section{Sample High-Fidelity Markdown Synthesis}
Figure \ref{fig:md_example} illustrates the output of our custom Markdown synthesis engine for a representative Form 4 filing. Note the preservation of tabular structures and the explicit linkage between numeric fields and footnote markers.

\begin{figure*}[ht]
\begin{lstlisting}[language=Python, label={fig:md_example}, caption={HyperStreamDB Retrieval Logic and Resulting Markdown Synthesis (Accession: 0001127602-21-016253). (SGML Header + Filing)}]
import hyperstreamdb as hdb

# Initialize table and query accession
table = hdb.Table("/home/ralbright/projects/openedgar/hdb_data")
acc = "0001127602-21-016253"

# Perform hybrid retrieval with chunk sorting
results = table.query().filter(f"accession_number = '{acc}'").execute()
df = results.to_pandas().sort_values('chunk_index')

# Reconstruct unified markdown from Arrow-native streams
markdown = "\n\n".join(df['text'].dropna().astype(str).tolist())
print(markdown)

# --- OUTPUT ---
# ---
# title: SEC 4 Filing - HAVERTY FURNITURE COMPANIES INC
# accession_number: 0001127602-21-016253
# form_type: 4
# schema_version: X0306
# issuer_cik: 0000216085
# issuer_name: HAVERTY FURNITURE COMPANIES INC
# issuer_trading_symbol: HVT
# period_of_report: 2021-05-09
# not_subject_to_section_16: false
# rule_10b5_1_plan: false
# no_securities_owned: false
# ---
# 
# # SEC 4 Filing - HAVERTY FURNITURE COMPANIES INC
# 
# ## Reporting Owners
# ### Reporting Person: PALMER VICKI R
# * **CIK:** 0001142394
# * **Address:**
#   - 780 JOHNSON FERRY RD.
#   - SUITE 800
#   - ATLANTA, GA, 30342-
# * **Position(s):** Director
# 
# ## Table I - Non-Derivative Securities
# | Security | Date | Deemed Exec | Code | Form Type | A/D | Equity Swap | Timeliness | Shares | Price | Total Value | Owned After | Value After | Nature |
# | :--- | :--- | :--- | :--- | :--- | :--- | :--- | :--- | :--- | :--- | :--- | :--- | :--- | :--- |
# | Common Stock| 2021-05-09|| A | 4| A | 0 | | 428 [^1]| 46.63|| 49988| | D |
# | Common Stock| 2021-05-10|| A | 4| A | 0 | | 428 [^2]| 46.63|| 50416| | D |
# | Common Stock| 2021-05-10|| A | 4| A | 0 | | 1072 [^3]| 46.63|| 51488| | D |
# 
# ## Filing Remarks
# [NULL]
# 
# ## Footnotes
# [^1]: Annual stock grant pursuant to Non-Employee Director Compensation Plan for the 2020-2021 board year.
# [^2]: Annual stock grant pursuant to Non-Employee Director Compensation Plan.
# [^3]: Portion of annual retainer paid in stock pursuant to Non-Employee Director Compensation Plan.
# 
# ## Signatures
# | Signature Name | Date |
# | :--- | :--- |
# | Jenny H. Parker, Attorney-in-Fact | 2021-05-11 |
\end{lstlisting}
\end{figure*}

\newpage
\section{Full Field-Level Extraction Metrics (Qwen3-Coder-30B-A3B)}
The following table provides the exhaustive precision, recall, and F1-score for all 137 fields evaluated in the 1,638-filing sample set using the Qwen3-Coder-30B-A3B model.

\begin{small}
\begin{longtable}{lcccc}
\caption{Exhaustive Field-Level Metrics (N=1,638 Filings)} \label{tab:full_metrics} \\
\toprule
\textbf{Field Name} & \textbf{Precision} & \textbf{Recall} & \textbf{F1-Score} & \textbf{Support} \\
\midrule
\endfirsthead
\toprule
\textbf{Field Name} & \textbf{Precision} & \textbf{Recall} & \textbf{F1-Score} & \textbf{Support} \\
\midrule
\endhead
\bottomrule
\endfoot
date\_of\_original\_submission & 0.417 & 1.000 & 0.588 & 5 \\
derivative\_holdings\_conversion\_or\_exercise\_price & 0.477 & 0.956 & 0.636 & 204 \\
derivative\_holdings\_conversion\_or\_exercise\_price\_fn & 0.416 & 0.776 & 0.541 & 49 \\
derivative\_holdings\_direct\_or\_indirect\_ownership & 0.499 & 0.975 & 0.660 & 204 \\
derivative\_holdings\_exercise\_date & 0.456 & 0.922 & 0.610 & 51 \\
derivative\_holdings\_exercise\_date\_fn & 0.536 & 0.938 & 0.682 & 160 \\
derivative\_holdings\_expiration\_date & 0.528 & 0.950 & 0.679 & 100 \\
derivative\_holdings\_expiration\_date\_fn & 0.419 & 0.938 & 0.579 & 48 \\
derivative\_holdings\_nature\_of\_ownership & 0.145 & 0.364 & 0.207 & 11 \\
derivative\_holdings\_nature\_of\_ownership\_fn & 0.783 & 1.000 & 0.878 & 9 \\
derivative\_holdings\_security\_title & 0.668 & 0.995 & 0.800 & 204 \\
derivative\_holdings\_security\_title\_fn & 0.135 & 1.000 & 0.237 & 7 \\
derivative\_holdings\_shares\_owned\_following\_transaction & 0.653 & 0.980 & 0.784 & 204 \\
derivative\_holdings\_shares\_owned\_following\_transaction\_fn & 0.652 & 0.938 & 0.769 & 16 \\
derivative\_holdings\_underlying\_security\_shares & 0.639 & 0.961 & 0.768 & 204 \\
derivative\_holdings\_underlying\_security\_shares\_fn & 0.333 & 0.875 & 0.483 & 8 \\
derivative\_holdings\_underlying\_security\_title & 0.659 & 0.995 & 0.792 & 200 \\
derivative\_holdings\_underlying\_security\_value & 0.666 & 1.000 & 0.800 & 204 \\
derivative\_holdings\_value\_owned\_following\_transaction & 0.656 & 0.985 & 0.787 & 204 \\
derivative\_transactions\_conversion\_or\_exercise\_price & 0.871 & 0.861 & 0.866 & 1,063 \\
derivative\_transactions\_conversion\_or\_exercise\_price\_fn & 0.882 & 0.842 & 0.862 & 546 \\
derivative\_transactions\_direct\_or\_indirect\_ownership & 0.976 & 0.960 & 0.968 & 1,063 \\
derivative\_transactions\_direct\_or\_indirect\_ownership\_fn & 0.333 & 0.800 & 0.471 & 5 \\
derivative\_transactions\_equity\_swap\_involved & 0.982 & 0.970 & 0.976 & 1,063 \\
derivative\_transactions\_exercise\_date & 0.726 & 0.781 & 0.752 & 187 \\
derivative\_transactions\_exercise\_date\_fn & 0.818 & 0.699 & 0.754 & 941 \\
derivative\_transactions\_expiration\_date & 0.774 & 0.701 & 0.736 & 521 \\
derivative\_transactions\_expiration\_date\_fn & 0.831 & 0.724 & 0.774 & 568 \\
derivative\_transactions\_nature\_of\_ownership & 0.470 & 0.520 & 0.494 & 75 \\
derivative\_transactions\_nature\_of\_ownership\_fn & 0.855 & 0.914 & 0.884 & 58 \\
derivative\_transactions\_security\_title & 0.969 & 0.956 & 0.962 & 1,063 \\
derivative\_transactions\_security\_title\_fn & 0.297 & 0.870 & 0.443 & 69 \\
derivative\_transactions\_shares\_owned\_following\_transaction & 0.957 & 0.945 & 0.951 & 1,063 \\
derivative\_transactions\_shares\_owned\_following\_transaction\_fn & 0.947 & 1.000 & 0.973 & 54 \\
derivative\_transactions\_transaction\_acquired\_disposed\_code & 0.979 & 0.963 & 0.971 & 1,063 \\
derivative\_transactions\_transaction\_code & 0.983 & 0.967 & 0.975 & 1,063 \\
derivative\_transactions\_transaction\_date & 0.983 & 0.967 & 0.975 & 1,063 \\
derivative\_transactions\_transaction\_date\_fn & 0.917 & 1.000 & 0.957 & 11 \\
derivative\_transactions\_underlying\_security\_shares & 0.948 & 0.936 & 0.942 & 1,063 \\
derivative\_transactions\_underlying\_security\_shares\_fn & 0.535 & 0.692 & 0.603 & 39 \\
derivative\_transactions\_underlying\_security\_title & 0.833 & 0.717 & 0.771 & 1,063 \\
derivative\_transactions\_underlying\_security\_title\_fn & 0.647 & 0.786 & 0.710 & 14 \\
derivative\_transactions\_underlying\_security\_value & 0.808 & 0.696 & 0.748 & 1,063 \\
derivative\_transactions\_value\_owned\_following\_transaction & 0.947 & 0.935 & 0.941 & 1,063 \\
footnotes\_1 & 0.993 & 0.990 & 0.991 & 1,468 \\
footnotes\_10 & 1.000 & 1.000 & 1.000 & 16 \\
footnotes\_11 & 1.000 & 1.000 & 1.000 & 11 \\
footnotes\_12 & 1.000 & 1.000 & 1.000 & 7 \\
footnotes\_13 & 1.000 & 1.000 & 1.000 & 4 \\
footnotes\_14 & 1.000 & 1.000 & 1.000 & 2 \\
footnotes\_2 & 0.993 & 0.992 & 0.993 & 954 \\
footnotes\_3 & 0.991 & 0.988 & 0.989 & 582 \\
footnotes\_4 & 0.993 & 0.992 & 0.992 & 357 \\
footnotes\_5 & 0.997 & 0.995 & 0.996 & 199 \\
footnotes\_6 & 0.992 & 0.992 & 0.992 & 119 \\
footnotes\_7 & 0.986 & 0.986 & 0.986 & 69 \\
footnotes\_8 & 1.000 & 1.000 & 1.000 & 43 \\
footnotes\_9 & 1.000 & 1.000 & 1.000 & 29 \\
form\_type & 0.997 & 0.995 & 0.996 & 1,639 \\
is\_rule\_10b5\_plan & 0.998 & 0.998 & 0.998 & 1,639 \\
issuer\_cik & 0.997 & 0.995 & 0.996 & 1,639 \\
issuer\_name & 0.995 & 0.992 & 0.993 & 1,639 \\
issuer\_schema\_version & 0.776 & 0.992 & 0.871 & 1,044 \\
issuer\_trading\_symbol & 0.774 & 0.992 & 0.870 & 1,033 \\
no\_securities\_owned & 1.000 & 1.000 & 1.000 & 1,639 \\
non\_derivative\_holdings\_direct\_or\_indirect\_ownership & 0.903 & 0.925 & 0.914 & 683 \\
non\_derivative\_holdings\_direct\_or\_indirect\_ownership\_fn & 0.413 & 0.464 & 0.437 & 28 \\
non\_derivative\_holdings\_nature\_of\_ownership & 0.746 & 0.725 & 0.735 & 542 \\
non\_derivative\_holdings\_nature\_of\_ownership\_fn & 0.779 & 0.763 & 0.771 & 152 \\
non\_derivative\_holdings\_security\_title & 0.949 & 0.993 & 0.970 & 683 \\
non\_derivative\_holdings\_security\_title\_fn & 0.433 & 0.867 & 0.578 & 15 \\
non\_derivative\_holdings\_shares\_owned\_following\_transaction & 0.934 & 0.981 & 0.957 & 683 \\
non\_derivative\_holdings\_shares\_owned\_following\_transaction\_fn & 0.705 & 0.981 & 0.820 & 106 \\
non\_derivative\_holdings\_value\_owned\_following\_transaction & 0.948 & 0.996 & 0.971 & 683 \\
non\_derivative\_transactions\_direct\_or\_indirect\_ownership & 0.985 & 0.976 & 0.981 & 2,544 \\
non\_derivative\_transactions\_direct\_or\_indirect\_ownership\_fn & 0.637 & 0.706 & 0.670 & 51 \\
non\_derivative\_transactions\_equity\_swap\_involved & 0.996 & 0.995 & 0.996 & 2,544 \\
non\_derivative\_transactions\_nature\_of\_ownership & 0.581 & 0.600 & 0.590 & 360 \\
non\_derivative\_transactions\_nature\_of\_ownership\_fn & 0.947 & 0.949 & 0.948 & 216 \\
non\_derivative\_transactions\_price & 0.996 & 0.995 & 0.996 & 2,544 \\
non\_derivative\_transactions\_price\_fn & 0.956 & 0.980 & 0.968 & 834 \\
non\_derivative\_transactions\_security\_title & 0.996 & 0.995 & 0.996 & 2,544 \\
non\_derivative\_transactions\_security\_title\_fn & 0.937 & 0.988 & 0.962 & 83 \\
non\_derivative\_transactions\_shares & 0.996 & 0.995 & 0.996 & 2,544 \\
non\_derivative\_transactions\_shares\_fn & 0.914 & 0.975 & 0.944 & 733 \\
non\_derivative\_transactions\_shares\_owned\_following\_transaction & 0.995 & 0.994 & 0.995 & 2,544 \\
non\_derivative\_transactions\_shares\_owned\_following\_transaction\_fn & 0.990 & 0.986 & 0.988 & 358 \\
non\_derivative\_transactions\_transaction\_acquired\_disposed\_code & 0.996 & 0.995 & 0.996 & 2,544 \\
non\_derivative\_transactions\_transaction\_acquired\_disposed\_code\_fn & 0.952 & 1.000 & 0.976 & 10 \\
non\_derivative\_transactions\_transaction\_code & 0.996 & 0.995 & 0.996 & 2,544 \\
non\_derivative\_transactions\_transaction\_date & 0.996 & 0.995 & 0.996 & 2,544 \\
non\_derivative\_transactions\_transaction\_date\_fn & 0.971 & 1.000 & 0.985 & 17 \\
non\_derivative\_transactions\_transaction\_total\_value & 0.976 & 0.974 & 0.975 & 2,544 \\
non\_derivative\_transactions\_value\_owned\_following\_transaction & 0.987 & 0.986 & 0.987 & 2,544 \\
not\_subject\_to\_section\_16 & 0.992 & 0.992 & 0.992 & 1,639 \\
period\_of\_report & 0.997 & 0.995 & 0.996 & 1,639 \\
remarks & 0.981 & 0.981 & 0.981 & 106 \\
reporting\_owners\_cik & 0.997 & 0.995 & 0.996 & 1,768 \\
reporting\_owners\_city & 0.985 & 0.983 & 0.984 & 1,761 \\
reporting\_owners\_good\_address & 0.997 & 0.995 & 0.996 & 1,768 \\
reporting\_owners\_is\_10pctowner & 0.997 & 0.995 & 0.996 & 1,768 \\
reporting\_owners\_is\_director & 0.995 & 0.993 & 0.994 & 1,768 \\
reporting\_owners\_is\_director\_nominee & 0.998 & 0.995 & 0.997 & 1,768 \\
reporting\_owners\_is\_officer & 0.998 & 0.995 & 0.997 & 1,768 \\
reporting\_owners\_is\_other & 0.998 & 0.995 & 0.997 & 1,768 \\
reporting\_owners\_name & 0.995 & 0.992 & 0.993 & 1,768 \\
reporting\_owners\_non\_us\_address\_flag & 0.961 & 0.959 & 0.960 & 1,768 \\
reporting\_owners\_officer\_title & 0.966 & 0.964 & 0.965 & 940 \\
reporting\_owners\_other\_text & 0.548 & 1.000 & 0.708 & 20 \\
reporting\_owners\_state & 0.991 & 0.987 & 0.989 & 1,758 \\
reporting\_owners\_state\_description & 0.012 & 0.171 & 0.022 & 41 \\
reporting\_owners\_zip & 0.991 & 0.990 & 0.990 & 1,755 \\
signatures\_signature\_date & 0.996 & 0.995 & 0.996 & 1,737 \\
signatures\_signature\_name & 0.995 & 0.994 & 0.995 & 1,737 \\
\end{longtable}
\end{small}

\noindent \textbf{Note on Zero-Support Fields:} Several fields in the Form 4 schema (e.g., \texttt{issuer\_foreign\_trading\_symbol}, \texttt{derivative\_transactions\_transaction\_timeliness}, \texttt{non\_derivative\_transactions\_transaction\_form\_type}) were not present in any of the 1,638 filings in our 2021 test set. These fields were correctly omitted by the LLM and are excluded from Table \ref{tab:full_metrics} to maintain focus on observed data distributions.

\end{document}